### 2020-11-10 doc/manuscript/Dow_manuscript.Rmd
update figs

**Title:** Effect of spring temperatures on tree growth phenology in two temperate deciduous forests

@@

pheno_Tsensitivity_caption <- "Figure 4. Relationship between DOY and climwin mean temperatures. For each 
observed climwin mean temperature value, the posterior mean of the fitted day of year
is represented by the solid blue line and credible intervals are represented by bands."

@@

```{r pheno_Tsensitivity, out.width="100%", echo=FALSE, fig.align="center", fig.cap=pheno_Tsensitivity_caption}
# Created in RScripts/bert/wood_phenology_analysis_bert.R
knitr::include_graphics("tables_figures/pheno_Tsensitivity_scbi.png")
```

```{r , out.width="100%", echo=FALSE, fig.align="center", fig.cap="Harvard. FIGURES WILL NEED TO BE COMBINED"}
# Created in RScripts/bert/wood_phenology_analysis_bert.R
knitr::include_graphics("tables_figures/pheno_Tsensitivity_HF.png")
```

>>>>

**Title:** ~~Effect of spring temperatures on tree growth phenology in two temperate deciduous forests~~
Warmer spring temperatures in temperate deciduous forests cause earlier tree growth but have little/only modest(?) effect on annual woody productivity

@@

pheno_Tsensitivity_caption <- "Figure 4. Relationship between growth parameters and climwin mean temperatures. For each 
observed climwin mean temperature value, the posterior mean of the fitted day of year
is represented by the solid blue line and credible intervals are represented by bands."

@@

```{r pheno_Tsensitivity, out.width="100%", echo=FALSE, fig.align="center", fig.cap=pheno_Tsensitivity_caption}
# Created in RScripts/bert/wood_phenology_analysis_bert.R
knitr::include_graphics("tables_figures/pheno_Tsensitivity_combo.png")
```
